\section{}\index{taxis!finding} \index{methods!GPS}   that allows me to connect and match with cabs that are available and through a gps connection match my location \index{Alina\ G.}
\section{}allows me to view 311 data (e.g. complaints) for buildings,  streets,  and neighborhoods to factor into apt hunting process. \index{\index{Andrew J.}}\index{Andrew J.}
\section{}can submit 311 requests with pictures,  audio and video. \index{\index{Saul S.}}\index{Saul S.}
\section{}allows me to view 411 data for buildings,  streets,  and neighborhoods to factor into my decision process when looking for an apartment. \index{\index{Unknown}}\index{Unknown}
\section{}provides a digitized version of the NYC Green Book,  so I have a 21st century rolodex of everyone I need to contact in city government. \index{\index{Philip A.}Philip A.}\index{Philip A.}Philip A.
\section{}takes the bus timetables and sets them to music, \index{Rohan G.}Rohan G.. \index{}
\section{}\index{map!of pet policies}shows you buildings and apartments and their actual specific pet policies (on a map w/ other normal/expected real estate info), \index{Ruthie V.}Ruthie V.. \index{}
\section{}\index{GPS!for reporting issues at current location}NYC\_QC  See a traffic light that's out; NYC\_QC,  see a trash bin overflowing; NYC\_QC,   GPS location,  time,  date,  photo. done!. \index{mike b.}mike b.
\section{}\index{map!for bicyclists}is like Google Maps for bicyclists,  but instead it maps out the optimal bike routes,  paths,  and streets to take based on date and time of da. \index{Richard T.}Richard T.
\section{}Warns New Yorkers where the most foot traffic is occuring so they can avoid traffic caused by tourist aimlessly walking while reading maps.. \index{Sigourney W.}Sigourney W.
\section{}tells me what hotels have reported bed bugs based on my geographic location.. \index{Paul N.}Paul N.
\section{}makes store locators work better for NYC-- e.g. includes cross streets in all results,  and can search within X blocks instead of X miles. \index{Margaret F.}Margaret F.
\section{}is zipcar for bikes.. \index{Randy L.}Randy L.
\section{}has a augmented reality tour guide of buildings,  parks and historical sites. \index{\index{Saul S.}}\index{Saul S.}
\section{}creates a social network within apartment buildings,  allowing for better communication and easier transitions for new tenants.. \index{Michael S.}Michael S.
\section{}\index{buildings!when built} \index{map!of buildings by age}maps when buildings were built and who was the architect based on my location.. \index{Edwin A.}Edwin A.
\section{}\index{taxis!going to Brooklyn}lets me narc on cab drivers who won't take me to Brooklyn. \index{Daniel S.}Daniel S.
\section{}\index{taxis!going to Brooklyn}will call a cab driver who will agree to take me to \index{boroughs!Brooklyn}Brooklyn at night.. \index{Jaime H.}Jaime H.
\section{}has the locations and conditions of all city dog runs. And information of any dog injurys  or deaths.. \index{Chad R.}Chad R.
\section{}\index{dogs}\index{map!of doggy intensity}I want an NYC app that is all about dogs! Dog-friendly parks and public spots,  check-in-based heatmaps for dog runs. \index{ meet-up scheduling for doggie playdates.  Carla E.} meet-up scheduling for doggie playdates.  Carla E.
\section{}\index{driving!parking} shows the vacant  space available in public parking lots in realtime. \index{Ming Y.}Ming Y.
\section{}\index{driving!parking}shows me where on street parking is available in as real time as possible. \index{Jason  T.}Jason  T.
\section{}\index{driving!parking}shows me where the cheapest parking lot is based on where I am at that moment. \index{Jason  T.}Jason  T.
\section{}\index{driving!rental cars}I want an NYC app that shows the nearest Hertz connect and/or Zipcar locations with available vehicles within a short walking distance  \index{Sheryl C.} Sheryl C.
\section{}\index{emergencies} Can help me in a time of emergency.. \index{James T.}James T.
\section{}\index{emergencies} Let's me know what I should do in an emergency and knows the strategy appropriate for my location and situation.. \index{Susan R.}Susan R.
\section{}\index{emergencies} tells me my options during an emergency based on where I am and what my status is (lost/hurt/trapped/OK).. \index{Kelly T.}Kelly T.
\section{}\index{Empire State building colors}tells what the colors of empire state building lights mean that day. \index{Kyri S.}Kyri S.
\section{}\index{find the closest!bus and taxi}\index{bus!location of}can locate the nearest available taxi and bus based on my location. \index{\index{Saul S.}}\index{Saul S.}
\section{}\index{find the closest!green space}shows me where the closest local green spaces are. \index{Nicholas C.}Nicholas C.
\section{}\index{find the closest!Greencart}tells me where the closest greencart (fresh fruit) is.. \index{alex n.}alex n.
\section{}\index{find the closest!indie theater}tracks all Indie Theater and lets you choose either closest to you or by type,  cost,  show title or length.. \index{Rhonda D.}Rhonda D.
\section{}\index{find the closest!livery car} \index{taxis!finding}lists car services closest to me. \index{Jessica K.}Jessica K.
\section{}\index{find the closest!livery car} \index{taxis!finding}lists the livery car services closest to me,  wherever I am throughout the five boroughs.. \index{Celina D.}Celina D.
\section{}\index{find the closest!non-Starbucks coffee} tells me where the closest non-Starbucks coffee shop is.. \index{Anna H.}Anna H.
\section{}\index{find the closest!NYC attractions}from any pt n NYC,  shows me what the closest NYC attractions r \& what the approx waiting times r (where applicable) for those attractions.. \index{Joe S.}Joe S.
\section{}\index{find the closest!restroom}shows me where the nearest public restroom is.. \index{Angie H.}Angie H.
\section{}\index{find the closest!theatres}shows me where the closest plays/theaters are and how I can buy tix on the fly. \index{Nicholas C.}Nicholas C.
\section{}\index{find!ugliest and dirtiest places}will show me  the ugliest and dirtiest  places in New York and propose how to make them better.. \index{\index{Jose H.}Jose H.}\index{Jose H.}Jose H.
\section{}\index{help me decide!best rooftop bar by day and night}shows panorama photos (day,  night,  and seasons) of every rooftop bar in NYC so we can all decide which view we want to see and which is best. \index{Ian H.}Ian H.
\section{}\index{help me decide!switch to the express or stay on the local}tells me whether I should switch to the express subway or stay on the local one (given my destination station).. \index{Ignacio O.}Ignacio O.
\section{}\index{help me decide!to drive or take transit}shows real time traffics and availability of vacant street parking spots,  and help me decide if I should be driving or taking public transit. \index{Ryo P.}Ryo P.
\section{}\index{intuitive!detection of car crashes} \index{intuitive!auto-despatch of ambulance if hard impact detected}auto-detects a car accident (based on phone gyroscope). Auto-sends police,  auto-sends ambulance if impact was hard.. \index{Justin H.}Justin H.
\section{}\index{intuitive!detection of gunshot locations}uses audio and ultra-precise timestamps to locate source of gun shots and automatically send police.. \index{Justin H.}Justin H.
\section{}\index{intuitive!detection of trapped elevators}uses the gyroscope to auto-detect when you're trapped in an elevator. (You went fast up or down,  stopped,  and then went nowhere). \index{Justin H.}Justin H.
\section{}\index{map!of public cameras}Has a map of all city public cameras,  whether it be red light,  traffic,  or safety cameras.. \index{Chad R.}Chad R.
\section{}\index{map!of AIA guide} \index{buildings!on a map}overlays the AIA guide to New York City buildings over a Google Map.. \index{Ahuman P.}Ahuman P.
\section{}\index{map!of bus and train in realtime}\index{bus!location of}let's me know when the next bus/train is  coming so that i can schedule accordingly. This would show up as a map to show its actual location. \index{Javi A.}Javi A.
\section{}\index{map!for Android}NYC Map Portal for Android. So much better than Google or Hotspot.. \index{Janine M.}Janine M.
\section{}\index{map!of landmarks}shows NYC landmarks and interesting info about them on a map. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}\index{map!of social services}shows social services (by program type) and community based orgs available on a map by location. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}\index{market approaches!bid on available parking}shows available parking spaces and allows drivers to bid on them in real-time (either by current availability or by time slots)... \index{Thomas D.}Thomas D.
\section{}\index{meta}allows me to submit ideas,  but first checks to see if the idea has already been submitted ;). \index{\index{Philip A.}Philip A.}\index{Philip A.}Philip A.
\section{}\index{methods!intuitive} \index{benefits!time saving} \index{crowds!avoiding}I want an NYC app that learns my travel patterns around the city,  compares that to aggregate behavior. \index{ and suggests ways for me to change to save time + avoid crowds} and suggests ways for me to change to save time + avoid crowds
\section{}\index{Metrocard!check balance}lets you check the balance of your Metrocard either by typing in the serial number on the card or by taking a photo of it.. \index{Alex T.}Alex T.
\section{}\index{Metrocard!check balance}tells me how much money I have left on my Metrocard.. \index{Senad L.}Senad L.
\section{}\index{morbid}uses public obituaries and death records to signal the possible opening of real estate for sale or apartments for rent.. \index{Rob M.}Rob M.
\section{}\index{New York!measure of how much a New Yorker you are} rangs how much a New Yorker a person is,  based on the places they visit,  eat,  and activities they attend.. \index{Luis M.}Luis M.
\section{}\index{panic button}Has a panic button that alerts the police when I feel in danger,  giving my location and number so they can call or come to check up on me.. \index{Sebastien M.}Sebastien M.
\section{}\index{parking!find free spots}will tell me when and where i can find free spots to park around NY.. \index{\index{Jose H.}Jose H.}\index{Jose H.}Jose H.
\section{}\index{parking!paying violations}lets anyone dispute or pay a parking violation/ticket by submitting photos and geotagging the location. \index{Judith R.}Judith R.
\section{}\index{participation!rating} I want an NYC app that lets us vote on the quality and condition of streets in NYC and based on the votes of users and residents. \index{ speed up the repairs as needed.  Kiran G.} speed up the repairs as needed.  Kiran G.
\section{}\index{report!clean restrooms}Shows the location of clean,  usable restrooms (whether at businesses or public) and allows users to report cleanliness,  safety,  etc.. \index{David M.}David M.
\section{}\index{report!danger for road users}allows users to report to NYC 311 dangerous places for pedestrians,  cycles,  cars ... in the st or sidewalks (w/ a photo,  geo \& description). \index{Matthieu M.}Matthieu M.
\section{}\index{report!in-progress crime} \index{crime!in progress}allows me to report any crime in progress with the ability to send a geotagged photo,  video,  and/or a description of the situation.. \index{Benjamin H.}Benjamin H.
\section{}\index{report!landlords}That is a yelp for apartment buildings,  where we can rate and report rents,  landlords and mgmt companies,  and offers other great insights. \index{gautam b.}gautam b.
\section{}\index{report!lawbreaking cab drivers}allows me to report cab drivers who break the law rather than calling 311 and waiting.. \index{Megan C.}Megan C.
\section{}\index{report!noise violations}allows users to report violations like noise,  health and safety in their apartments,  streets and/or workplace. \index{Deborah R.}Deborah R.
\section{}\index{report!police brutality}allows me and other witnesses to report / submit evidence of abuse and/or brutality by police officers. \index{Mike P.}Mike P.
\section{}\index{report!potholes}\index{GPS!reporting potholes with}reports pothole by taking a picture of it with iPhone/Android and records GPS coordinates. \index{Rene S.}Rene S.
\section{}\index{report!problems with infrastructure}\index{GPS!report infrastructure problems}enables users to report problems with infrastructure like potholes,  broken equipment in parks,  etc. by using GPS and accepting photos. \index{Deborah R.}Deborah R.
\section{}\index{report!problems with MTA}lets you submit reports,  complaints,  issues directly to the MTA and lets you know if they're being addressed.. \index{stephen m.}stephen m.
\section{}\index{report!public mood}reports the mood of a crowd in an area based on witness accounts. Late trains =angry crowd. Yankees beat Boston,  happy crowd.. \index{Dave T.}Dave T.
\section{}\index{report!rats}allows residents to report rats sightings based on geo-location. \index{Sze C.}Sze C.
\section{}\index{report!reckless cab drivers}monitors your gyroscope data to auto-identify reckless cab drivers. (Detect and report the cab drivers bluetooth ID)). \index{Justin H.}Justin H.
\section{}\index{report!situations}\index{crime!report by shaking phone}that reports situations fast, i.e., hazards, accidents, crime by simply shaking a phone.Several shakes from a location leads to inference/action. \index{Vasu S.}Vasu S.
\section{}\index{report!taxi refusal due to destination in other borough}can report a complaint when a taxi refuses to pick you up because your destination in one of the five boroughs,  pic of license \# uploadable.. \index{Crystal  V.}Crystal  V.
\section{}\index{report!taxi service refusal}allows New Yorkers to report cab drivers that refuse them service. Snap a photo of the license or plate,  submit.. \index{Tom C.}Tom C.
\section{}\index{restrooms!sanitary ranking}shows nearby sanitary washroom by means of ranking and allows for votes.. \index{Kosuke N.}Kosuke N.
\section{}\index{restrooms} I want an NYC app that for each borough gives the location of nearest public restrooms with A,  B,  C. \index{ D type ratings for their cleanliness and the level of safety \index{restrooms!safety of} \index{crime!in restrooms}  \index{Sheryl C.} Sheryl C.} D type ratings for their cleanliness and the level of safety \index{restrooms!safety of} \index{crime!in restrooms}  \index{Sheryl C.} Sheryl C.
\section{}\index{safari for the attractive}shows me where the most good-looking people are! Like a safari for the attractive!. \index{Joel K.}Joel K.
\section{}\index{sharing!phone battery in the subway}let me share phone battery specially in the subway. \index{Valentina C.}Valentina C.
\section{}\index{sharing!taxi rides}helps me find cabbies that really go to outside borrows and/or allow me to find people for cab sharing. \index{Sebasitan W.}Sebasitan W.
\section{}\index{shopping!location of sales} \index{shopping!sample sales}I want an NYC app that Tells you were all the current retail sales are including sample sales  Dana H.
\section{}\index{taxi!billing}I want an NYC app that calls my taxi account and bills me appropiately fo my pickup and associated destination.  Diane C.
\section{}\index{taxi!sharing} enables NYCers to share taxis to NYC airports. 1st user sets departure location,  time and 2nd user(s) can check in and meets 1st user there.. \index{Eduardo M.}Eduardo M.
\section{}\index{taxis!fare calculator} Tells me how much I should really be paying for non  yellow taxi cabs. \index{Hillary M.}Hillary M.
\section{}\index{taxis!fare calculator}estimates Taxi fares using live traffic info and distance markers.. \index{Lindsey W.}Lindsey W.
\section{}lets people post how much they just paid for a limo/black car so they can compare fares and complain about attempts to overcharge. \index{Rudolf V.}Rudolf V.
\section{} \index{taxis!rental}\index{GPS!find a taxi with}helps visitors/residents get a taxi by letting them hail a cab through their phone \& sending prompts to nearby cabbies via text/sound in GPS. \index{Rudolf V.}Rudolf V.
\section{}makes it easy to find people to share taxi rides from/to the airports.. \index{Micah F.}Micah F.
\section{}tells me where decent iced coffee is at the carts.  They're really hit and miss but sometimes I don't have time to wait at Dunkin/Starbucks. \index{Dave T.}Dave T.
\section{}with live data lets you know wait times at restaurants that you can't book at.. \index{Ben S.}Ben S.
\section{}allows you to check into appointments,  get a number and updates you on your status,  so that you don't have to wait in line. (Example: DMV). \index{James F.}James F.
\section{}show me how long exactly I do have to wait until the rain will stops,  based on my current location in a city.. \index{Stepa M.}Stepa M.
\section{}\index{GPS!as a tour guide}Acts as a tour guide- uses gps to determine location and provides audio and visual acts about historic locations nearby.. \index{Theresa G.}Theresa G.
\section{}acts as my metrocard and allows me to buy refills or offers auto refilling.. \index{Laura D.}Laura D.
\section{}Add QRcode 2 official parking placards so ppl can geotag the parked car and have it linked 2 a site.ONLY  officials can see loc to End Abuse. \index{Mzansi P.}Mzansi P.
\section{}\index{GPS!to find building information}aggregates all the information one can get about a building/house in one place using GPS to automatically determine the BBL.. \index{Paul G.}Paul G.
\section{}aggregates all the volunteer initiatives available,  its cause and allows me to register/participate. \index{Christopher B.}Christopher B.
\section{}aggregates bike accident data to make/help petition for safer bike routes. \index{Trev E.}Trev E.
\section{}\index{alert me!coffee} alerts me to a nearby location with a free table,  a strong wifi signal,  and a decent cup of coffee.. \index{Will L.}Will L.
\section{}\index{alert me!causes} alerts me to current causes and projects related to my surroundings,  with information on how to help or join the movement.. \index{Christine P.}Christine P.
\section{}\index{alert me!city council hearing} alerts me when city council or other government entities are holding hearing,  publishing reports on categories I subscribe to.. \index{Randy L.}Randy L.
\section{}alerts residents of dangerous traffic intersections. \index{Sze C.}Sze C.
\section{}\index{alert me!apartment for rent nearby} alerts the user whenever there is an apartment for rent in the area that they are currently in.. \index{Sadman S.}Sadman S.
\section{}\index{alert me!beg bugs in businesses} \index{bed bugs!in businesses} alerts you to nearby businesses,  buildings,  etc. that have experienced recent bed bug problems (ick!).. \index{Anna H.}Anna H.
\section{}allows  input of  dial group feedback on video feeds of public discussion which is then aggregated \& graphically overlaid  on your device.. \index{BOKE A.}BOKE A.
\section{}\index{GPS!to sign up for street cleaning tasks}allows a user to use the GPS/location finder on their phones to sign up for comission based street cleaning \& anonymous reporting. \index{Rudolf V.}Rudolf V.
\section{}allows apps to work in the subway.. \index{Will L.}Will L.
\section{}allows average NYC-ers to invest \$\$\$ money in up-and-coming NYC-based start-ups. Think Kiva + Kickstarter,  but for angel investing.. \index{Richard T.}Richard T.
\section{}allows downloads directly from the New York Public Library eCollection to my phone,  Kindle,  and/or Nook.. \index{Tom C.}Tom C.
\section{}\index{kids!voice opinions} allows kids to voice their opinion with the city on political issues and local matters.. \index{Will T.}Will T.
\section{}allows me to bid on meals while here.  I choose italian and price and restaurants text me their submissions and I approve or deny. \index{Andrew K.}Andrew K.
\section{}\index{GPS!find a taxi with}\index{taxis!find nearest}allows me to connect and match with cabs that are available and through a gps connection match my location. \index{Alina G.}Alina G.
\section{}allows me to create my own apps to implement my whizbang idea and share those apps with everybody else to customize as they please.. \index{Joel N.}Joel N.
\section{}\index{superhero powers!find everything inside Central Park} Allows me to find everything and anything inside central park.. \index{Albert R.}Albert R.
\section{}allows me to gain points for positive lifestyle choices - exercise,  volunteering,  recycling --  \& redeem them for rewards at NYC businesses.. \index{Laura D.}Laura D.
\section{}\index{report!noise complaint}allows me to instantly log a noise complaint with the city based on my current location.. \index{Will T.}Will T.
\section{}\index{report!homeless people} allows me to log location,  time,  and condition of homeless people and panhandlers i give change to,  to highlight their plight. \index{Anthony T.}Anthony T.
\section{}Allows me to manage MuniMeter parking cards: see balances,  recharge etc. Maybe eventually use the app to pay the meter instead of a card.. \index{Jonathan H.}Jonathan H.
\section{}allows me to market for sale items conveniently using social media,  and find potential buyers by location.. \index{Michael K.}Michael K.
\section{}allows me to rate the service and provide feedback of civil servants(Taxi,  DMV,  Post Office,  Policeman,  etc..) on a mobile device. \index{chung n.}chung n.
\section{}allows me to scan my parking tickets and either dispute or pay on the spot without having to use snail mail. \index{Yasmin F.}Yasmin F.
\section{}Allows me to see down though the streets down to the subway below our feet. \index{Robert L.}Robert L.
\section{}allows me to submit ideas for an NYC app and have others vote and comment on those ideas.. \index{Jonathan S.}Jonathan S.
\section{}allows me to submit photos to \index{agency!NYPD}NYPD of drivers violating city traffic laws (e.g. parking in the bike lane). \index{Evan T.}Evan T.
\section{}allows me to take a pitcure of graffiti (tagging) and send it to the city for cleanup.. \index{alex n.}alex n.
\section{}allows me to take my own personal walking tours with audio commentary.. \index{Albert R.}Albert R.
\section{}allows me to take pictures of motorists breaking the law (e.g. bike lane parking) and submit them to the \index{agency!NYPD}NYPD for ticketing. \index{Justin L.}Justin L.
\section{}Allows me to use my smartphone instead of all the loyalty cards I carry around!. \index{Eric L.}Eric L.
\section{}allows me to vote on issues before the city council,  city planning,  commisison,  borough boards,  and community boards.. \index{Thomas L.}Thomas L.
\section{}\index{vote on!public transportation}allows me to vote on the individual public transportation systems by casting a thumbs up or thumbs down metric via my Twitter account.. \index{Chance C.}Chance C.
\section{}allows my electronic devices to draw power from surges or some other device that can be found in local and private places. \index{Darrian G.}Darrian G.
\section{}allows my friends and I to geolocate music to different parts of the city so that I have a social-generated soundtrack of the NYC.. \index{Gene L.}Gene L.
\section{}allows my Metro Card to be on my smartphone,  so I don't keep reaching for it all the time!  Airlines have already figured this out!. \index{Jennie W.}Jennie W.
\section{}allows NYC DJ's to upload their DJ sets and then anyone in the world can enjoy the tunes. The App would be called NYC DJ's rule.. \index{Richard T.}Richard T.
\section{}allows NYC residents to barter and exchange used goods (clothing,  books,  electronics,  etc.) amongst themselves.. \index{Richard T.}Richard T.
\section{}allows NYC-ers to donate time and \$\$\$ to 'in-danger' public schools that are in dire need of supplies,  additional teachers,  and tutors.. \index{Richard T.}Richard T.
\section{}allows NYC-ers to submit questions on a monthly basis. Mayor then has to adress the top voted questions. App is called Virtual Town Hall.. \index{Richard T.}Richard T.
\section{}allows people in real time to find out when a parking spot becomes available on street. Users share when they leave a spot.. \index{Ian H.}Ian H.
\section{}allows people to check in at NYC public tennis courts,  check wait times and reserve hour long blocks on a particular court.. \index{Matt P.}Matt P.
\section{}allows ppl to suggest small fixes w/big impact they notice while delayed on the MTA,  like posting signs in the stairwell saying Keep Right. \index{Greg S.}Greg S.
\section{}allows residents to rate their building's owner,  mgmt co.,  landlord,  even brokers and lets interested renters browse those ratings.. \index{Bud C.}Bud C.
\section{}allows to use your mobile phone underground,  like you can do it in the rest of the world.. \index{Uwe B.}Uwe B.
\section{}allows tourists to find popular sightseeing places based on other tourists reviews (by demographics). \index{Sonny K.}Sonny K.
\section{}allows users to post what they pay for rent or paid in the past for specific apts.-tracks/records data - adds transparency/info for renters. \index{Jennifer K.}Jennifer K.
\section{}allows users to see what other NY'rs are doing around them in real-time. Sale nearby? Restaurant opening? If it's near me,  I want to know.. \index{Seth A.}Seth A.
\section{}Allows users to vote for the rudest,  most power-trippy bouncers and bar owners so we can avoid those places at all costs. \index{Ian H.}Ian H.
\section{}allows you to access news updates even when you're underground on the subway!. \index{Anna H.}Anna H.
\section{}allows you to hail a nearby cab with the push of a button.. \index{Anna H.}Anna H.
\section{}allows you to post questions (general,  events occuring,  discounts). The app also allows you to respond to people's questions in real time.. \index{James F.}James F.
\section{}allows you to refill your Metrocard before you get to the subway station (no lines or hassle necessary).. \index{Anna H.}Anna H.
\section{}allows you to search for the City official you want to contact,  basically an electronic Green Book.. \index{Gene R.}Gene R.
\section{}allows you to see what certain blocks,  neighborhoods,  buildings looked like 100 years ago.. \index{Anna H.}Anna H.
\section{}allows you to suggest businesses to go into vacant storefronts.. \index{Ahuman P.}Ahuman P.
\section{}An app that compiles what exhibits are at museums around the city and also categorizes them by period,  etc.. \index{Richard L.}Richard L.
\section{}Announces daily events by genre/ neighborhood (concerts,  festivals,  sales,  markets). \index{Alexander P.}Alexander P.
\section{}Announces/ helps organize volunteer opportunities in my neighborhood. \index{Alexander P.}Alexander P.
\section{}app that texts me trivia/information specific to where I currently am in the city.  Lesser known factual info.. \index{Andrew K.}Andrew K.
\section{}asks NYC residents to make a case against congestion pricing. \index{Sze C.}Sze C.
\section{}auto-connects users into a 'mesh' computer network,  which would expand the broadcast range of Wi-Fi sources.. \index{Justin H.}Justin H.
\section{}\index{GPS!find local properties to rent}by using GPS lets you know about available property to rent in the vicinity.. \index{Ben S.}Ben S.
\section{}calculates commute times based on current traffic reports.. \index{Rachel S.}Rachel S.
\section{}calculates how long it will take me to get from where I am to where I'm going by taxi,  subway or on foot based on time of day and traffic.. \index{David M.}David M.
\section{}calculates my daily carbon footprint and shows activities in NYC I can do to counteract my carbon footprint.. \index{James F.}James F.
\section{}calls my taxi account and bills me appropiately fo my pickup and associated destination.\index{Diane C.}  Diane C.
\section{}\index{bus!location of} \index{realtime!traffic}can give me real time traffic updates and bus, train, ferry schedule from my to and from location. \index{Craig C.}Craig C.
\section{}can log public grievances and \index{report!public grievances} law breakers like road needs repair,  public places not clean,  red light jumps,  rash driving,  neighborho. \index{Tarun B.}Tarun B.
\section{}\index{tell me!things I like to do}can note my schedule and hobbies/interest,  during my free time the app can tell my things I can do in NYC to fill up my free time.. \index{James F.}James F.
\section{}can search and scan some data within the contents of a pdf file. \index{ANSHAY A.}ANSHAY A.
\section{}can search apartments for lease or sublet with Google map location-also users can post apartment listing with location info and pictures. \index{Mayank Y.}Mayank Y.
\section{}\index{camera!point to get information}can tell give me the information around me just by pointing the camera (Augmented Reality). \index{Mohit A.}Mohit A.
\section{}\index{tell me!about crime}\index{crime!in a specific neighborhood}can tell me about crime in an specific neighborhood.. \index{Michael P.}Michael P.
\section{}\index{tell me!about landmarks}can tell me all the special land marks in NYC. \index{Albert R.}Albert R.
\section{}\index{animals!rats}can tell me in real-time street with rats to avoid them while walking. \index{Valentina C.}Valentina C.
\section{}can tell me when the next public event is and directions on how to register and directions.. \index{Albert R.}Albert R.
\section{}captures the essence of NYC and its diverse neighborhoods from every subway stop,  that is why we started to create \index{apps!referenced!468stops.com} www.468stops.com. \index{Rich W.}Rich W.
\section{}\index{public scorn}captures the license plate numbers of dangerous,  obnoxious drivers and subjects them to both legal accountability and public scorn.. \index{Bill M.}Bill M.
\section{}categorizes user generated pictures/video of NYC,  that can be shared,  printed,  and combined on a website that chronicles the City.. \index{Jason G.}Jason G.
\section{}clearly shows me the location of every single retailer in the city. \index{Johnson T.}Johnson T.
\section{}\index{best!places for having fun} collects insiders¬¥ tips of the best places in NYC for having fun,  enjoy the nature,  getting inspired or for having a great dinner.. \index{Leif Ole H.}Leif Ole H.
\section{}\index{crime!bad neighborhoods}combines crime stats with geolocation data,  to create 'bad neighborhood' alerts. \index{Reed M.}Reed M.
\section{}combines different review sites like yelp,  city search,  urban spoon,  google review in one app,  plus foursquare plugin for check ins \& deals. \index{Lars R.}Lars R.
\section{}communicates with trains by bluetooth that vibrates when the train stops at my destination.Sleeping/Drunk/lost people won't miss their stop. \index{Dave T.}Dave T.
\section{}compares my building's energy use to similar types of buildings nearby. \index{Matthew B.}Matthew B.
\section{}Compiles weekly  lists of museum,  gallery and public art exhibitions.. \index{lynn b.}lynn b.
\section{}\index{311!app overhaul} Completely overhauls the existing 311 app,  and is so useful that every New Yorker with a smartphone wants this app. \index{Luis M.}Luis M.
\section{}\index{sports!find a female jogging companion} connects joggers (especially women) so they do not jog alone in the city.. \index{Millicent M.}Millicent M.
\section{}connects neighbors and allows them to discover and share customized deals around the city.. \index{Craig E.}Craig E.
\section{}connects young adults on public assistance w/ ed programs that will help them succeed in the job mrkt. Why needed: http://ht.ly/5vxn3. \index{Joe S.}Joe S.
\section{}\index{apps!referenced!Groupon} \index{apps!referenced!LivingSocial} consolidates all of the local daily deals from sites like Groupon,  LivingSocial,  etc. in one location.. \index{Anna H.}Anna H.
\section{}contain a administrative portal dedicated to NYC,  that will directly relates with aspects and needs of NYC people with information they want. \index{Chetan B.}Chetan B.
\section{}contains all the info,  news,  statistics,  ranking,  and events at public schools. Also offers a way to donate/fundraise for school projects. \index{Luis M.}Luis M.
\section{}\index{GPS!nearby subway arrivals}Countsdown the arrival of a SUBWAY - GPS locates you and gives 5 and 2min warnings so you can catch it. \index{Craig P.}Craig P.
\section{}creates artwork without traditional fine art skills to decorate my house or office. http://bit.ly/qWoBws. \index{Paul S.}Paul S.
\section{}\index{bus!with cultural activities on board}creates flex buses that picks up passengers based on a NYC social network and features artistic,  musical  and educational themes on board.. \index{norman s.}norman s.
\section{}creates networks of citizens who can chime in their borough,  district and neighborhood issues with local government.. \index{Carlos J.  G.}Carlos J.  G.
\section{}crowdsources clean sidewalks. See trash. Take pic w/phone. Pick up trash. Take pic. Submit. Get reward - \$ or gold stars. Share w/friends!. \index{Jenna L.}Jenna L.
\section{}directs me to local merchants rather than big box stores for everyday products.. \index{Brian H.}Brian H.
\section{}\index{avoid!renting near construction}displays existing and future construction locations based on permits,  so I can avoid renting a place in earshot.. \index{Justin H.}Justin H.
\section{}disseminates transit data in real-time,  more efficiently and in one place that can propose alt routes/commutes based on service advisories!!. \index{Christopher B.}Christopher B.
\section{}does group purchase by demand instead of offer. 20 friends and I want cheap starbucks. Send them an offer for 15% off,  see if they take it. \index{Dave T.}Dave T.
\section{}\index{bus!low-tech method for location of}DRIVERS get an app that they leave on all day that tracks the position of the bus. RIDERS get an app that tells them where the buses are.. \index{Michael K.}Michael K.
\section{}easily displays restaurant/bar specials happy hours near my location and directions on how to get there.. \index{Alicia C.}Alicia C.
\section{}empowers parents \& teachers to raise readers using empirically sound methods so every child can succeed in school  \& life. \index{Melinda T.}Melinda T.
\section{}enables a chatroulette-esque feature to the taxi TVs. \index{Noah D.}Noah D.
\section{}\index{crime!broadcast news of}enables New Yorkers to broadcast/receive  breaking news at the click of a button. Ex: NYer sees violent crime,  wips out app,  and broadcasts.. \index{Costa M.}Costa M.
\section{}enables people to donate to charities they see in those taxi ad's during the ride,  using the same mechanism we use to pay for the ride.. \index{Luis M.}Luis M.
\section{}encourages residents to do good works for charities and those in need. \index{Sze C.}Sze C.
\section{}enlightens me to interesting tidbits of historical events and data based on my geolocation. \index{Will L.}Will L.
\section{}\index{bus!location of}estimates subway train and bus locations based on the printed schedules.. \index{Arseny A.}Arseny A.
\section{}extends the Key to the City art project from last summer to a mobile application where users can check-in and get insider info. \index{Sarah H.}Sarah H.
\section{}facilitates the renting of items between residents. Think \index{apps!referenced!Craigslist} craigslist for renting of personal and household goods.. \index{Ian H.}Ian H.
\section{}\index{interacting with!NYorkers} facilitiates interacting with NYorkers. It'd be cool 2 offer job advice/recipes/cafe spots/directions to youth/tourists/neighbors?. \index{Alberto C.}Alberto C.
\section{}finally gets apartment listings right,  with pics,  street anneighborhood info,  landlord info,  broker info transparency,  and community ratings. \index{Trev E.}Trev E.
\section{}finds apartments for rent based on price,  location and other criteria (i.e. elevator,  doorman,  etc).. \index{Rachel S.}Rachel S.
\section{}\index{restrooms!clean and free} finds me clean public restrooms for free. \index{Greg  G.}Greg  G.
\section{}\index{GPS!nearby cultural events}finds me on gps and tells me what cultural events are happening around me,  now and in the next few hours. \index{Merva F.}Merva F.
\section{}\index{ALL CAPS} FINDS OLD BICYCLES AND GIVE THEM TO UNDERPRIVILEGED YOUTHS. \index{Vimon R.}Vimon R.
\section{}finds the nearest subway entrance with an active booth agent and shows the number of working metrocard vending machines.. \index{Paola V.}Paola V.
\section{}finds the political rep related to any given place/location,  helps me communicate with them,  form citizen groups,  and discuss/rate reps. \index{Lance N.}Lance N.
\section{}for each borough gives the location of nearest public restrooms with A,  B,  C,  D type ratings for their cleanliness and the level of safety. \index{Sheryl C.}Sheryl C.
\section{}\index{tell me!where to run}generates running/walking/biking routes for me based on where I am and how far I want to go.. \index{alex n.}alex n.
\section{}geolacates me when I park,  shows me parking rules and alerts me before I need to move my car or commercial vehicle.. \index{Dana F.}Dana F.
\section{}geolocates me and let's me know if it's okay to park there at that time and until when it's free. \index{Divyesh D.}Divyesh D.
\section{}geolocates my phone and shows me what will be built at nearby construction sites. \index{Alex C.}Alex C.
\section{}gets your location \& plate number,  then lets you pay for parking by credit card through your phone. Nullifies parking ticket if written.. \index{Justin H.}Justin H.
\section{}\index{tell me!an inspirational daily quote}give inspirational daily quotes to remind people that better days are coming.. \index{Lissette R.}Lissette R.
\section{}\index{shopping!sales} gives a list of all the stores in nyc that are having sales.  Should be able to search by \% off,  location,  store type,  etc. \index{Eric M.}Eric M.
\section{}gives daily exercise and healthy eating tips,  plus a teenager version which could stop future obesity and health problems. \index{Carl W.}Carl W.
\section{}gives dates,  info,  and directions for festivals and other recreation events with options to sort by cost or free. \index{Franco C.}Franco C.
\section{}gives me discount deals on getaways  in NYC through Groupon and it's merger with Expedia. \index{Latoya C.}Latoya C.
\section{}gives me discounts through Groupon and  eating in NYC. \index{Latoya C.}Latoya C.
\section{}gives me discounts through groupon on hotels in NYC. \index{Latoya C.}Latoya C.
\section{}\index{tell me!health statistics}gives me NYC health statistics by borough and neighborhood.. \index{Celina D.}Celina D.
\section{}\index{Metrocard!get EZpass points from using} \index{EZpass!get points from using Metrocard} gives me points towards my EZ pass everytime I use my metrocard.. \index{Millicent M.}Millicent M.
\section{}gives tourists a REAL ever changing guide of where to eat \& hang out shared by real NYC residents. And not the touristy things.. \index{Jinny C.}Jinny C.
\section{}gives updates on local events,  castings,  entertainment ect.. \index{Darrian G.}Darrian G.
\section{}guides me through New York City landmarks,  providing the history of each landmark in multiple languages.. \index{Jennifer B.}Jennifer B.
\section{}guides me through the exhibits at NYC museums while I am there (replacing those rental headsets). \index{Sarah H.}Sarah H.
\section{}guides me to a food vendor that is offering a 'like' or 'check-in' worthy food special for \$5 or less at any given moment.. \index{Chance C.}Chance C.
\section{}has a calendar of all the running and biking events that close down NYC streets. \index{Dan K.}Dan K.
\section{}has a visual,  color coded map of all street parking rules,  regulations and street cleaning schedules.. \index{Will T.}Will T.
\section{}has allows residents to post free stuff that they don't want so that they're recycled.  Along with this,  a geo search app to find stuff!. \index{Vimal K.}Vimal K.
\section{}has an oral guide to the city + all city museums in one single place (no lines,  no hassle).. \index{Ignacio O.}Ignacio O.
\section{}Has nutrition information for all the NYC restaurants. \index{Zachary B.}Zachary B.
\section{}has up-to-date information on legislation being brought to vote,  and recent rulings,  etc.. \index{Deborah R.}Deborah R.
\section{}\index{sport!find buddy}help me find a buddy (a friend of a friend) to play (any sport) and if someone else can lend a place (e.g. their bldg racquet ball ct). \index{Sujay M.}Sujay M.
\section{}\index{sport!find running buddy}helps me find a running buddy for my spur of the moment runs. \index{Noah S.}Noah S.
\section{}helps me find the most prolific real estate agent - makes the best deals.. \index{Satjot S.}Satjot S.
\section{}\index{sport!find buddy}helps me finding places. \index{daniely v.}daniely v.
\section{}Helps me flag down a cab. It could send my location to nearby cabs based on GPS,  so they would know to drive past me.. \index{Ivete T.}Ivete T.
\section{}helps me to map running routes around the city/thru Central Park,  clearly showing mile markers and water fountains.. \index{Dorothy J.}Dorothy J.
\section{}\index{depressing!cost per sq foot of apartments}helps me track the cost per square foot of each apartment I visit when hunting for a new home.. \index{Randy L.}Randy L.
\section{}helps me,  and other New Yorkers,  determine: (1) which public services require volunteers,  (2) when,  and (3) what kind of assistance. \index{Jason G.}Jason G.
\section{}helps my sister reserve a cab (without fighting w/others over it) at 1:30am in SOHO.. \index{Tiffany K.}Tiffany K.
\section{}helps non-profits and public agencies accept donations for initiatives that help city residents. \index{Jason G.}Jason G.
\section{}Helps parents track the academic progress of their child,  and make recommendations for areas of improvement. \index{Luis M.}Luis M.
\section{}Helps students and parents choose which junior/high schools to apply for,  including the requirements,  concentrations,  and application dates. \index{Luis M.}Luis M.
\section{}helps students study,  learn,  and prepare for NY State standardized exams on their phone,  internet,  xbox/playstation networks..... \index{Luis M.}Luis M.
\section{}helps tenants to rate and review their apartment buildings and blocks,  and prospective buyers and renters to see those ratings/reviews. \index{Kostas A.}Kostas A.
\section{}\index{buildings!unbuilt} Highlights the sites of extraordinary architecture that was \_never\_ built.. \index{Jerome C.}Jerome C.
\section{}\index{superhero powers!time travel}  History - Tell us what used to be at this location? Now some other place is there.. \index{susan g.}susan g.
\section{}\index{just tell me what to do already}I can configure the app to look for my interests and I will receive emails or texts stating specials that coorelate to what I enjoy doing. \index{Andrew K.}Andrew K.
\section{}I can take a picture of graffiti in a particular location and send it to the city so they can clean it up.. \index{Supreet K.}Supreet K.
\section{}\index{camera!submit reports to right city agency}I can take my camera phone image and submit it to a NYC image site that can reroute it to the right city agency to fix the problem. \index{Chi  M.}Chi  M.
\section{}\index{avoid!long lines when voting} I want a NYC app that accepts the people of New York's vote during the political season whereby they avoid long lines and enjoy convienence(Save energy,  money). \index{\index{Unknown}}\index{Unknown}
\section{}I want a NYC app that shows me restaurants,  building fronts,  public places,  and other locations that have appeared in famous movies. \index{Unknown}Unknown
\section{}\index{GPS!to find out parking rules}I want a NYC mobile app that shows the real-time parking rules of a spot on a street through real-time GPS positioning. \index{Dan C.}Dan C.
\section{}\index{food truck locator}i want an app that shows foodtrucks with real-time locations,  w/ descriptions and ratings. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}I want an APP that tells you which train to take when train is rerouted or not running - especially on weekends. Deborah J.. \index{Harobed S.}Harobed S.
\section{}I want an NYC app that creates artwork without traditional fine art skills to decorate my house or office. http://bit.ly/qWoBws  Paul S.
\section{}\index{crime!nearby}I want an NYC app that shows recent crimes in your \index{methods!current location}current location along with pertinent info on the perps. Thanks.  Richard V.
\section{}I want to know hot destinations of this weekend. who want to go where and for what?. \index{Amir K.}Amir K.
\section{}I want to know who else around me suffers from strange headache?. \index{Amir K.}Amir K.
\section{}Identifies and locates public sculptures and significant architecture. \index{Robert S.}Robert S.
\section{}\index{avoid!smelly streets}identifies how much each street smells and allows you to plot the least smelly route through the city. \index{Richard L.}Richard L.
\section{}\index{bus!location of}in real-time shows me which bus is arriving at my stop and when it will get there.. \index{R B.}R B.
\section{}\index{bus!give kudos to drivers}incentivizes riders to publicly rate \& document MTA service,  give kudos to bus drivers,  phototag broken equipment,  \& track late buses.. \index{C B.}C B.
\section{}indicates the nearest alternate subway line--going my way--when I'm stuck at one that breaks down!. \index{Blanca C.}Blanca C.
\section{}Indicates the parking regulations street by street- alternate side,  no parking any time,  trucks loading and unloading,  muni meter,  no standi. \index{lynn b.}lynn b.
\section{}informs me when my laundry is done and ready for pickup,  and give me the option to have it delivered. \index{Luis M.}Luis M.
\section{}Informs parents when their child is absent from school. \index{Luis M.}Luis M.
\section{}\index{GPS!parking info}informs parking rules via gps realtime,  allows payment,  calculates and notifies timed parking,  and notifies any ticketing/towing in action.. \index{Crystal  S.}Crystal  S.
\section{}informs/reminds residents about their political representatives and provides an easy way to contact them/their offices.. \index{Scott K.}Scott K.
\section{}integrates with a sensor to eliminate the need (or length) for the LOUD \index{agency!MTA}MTA Subway emergency alarms when it is not a violation.. \index{Garry G.}Garry G.
\section{}is a conditional alarm clock. If the train is not running,  super bad weather,  or unusual activities it sets off an alarm to wake me up early. \index{Dave T.}Dave T.
\section{}\index{GPS!as tour guide}is a personal concierge or tour guide,  giving information on sights and entertainment in NYC or the immediate area using GPS or photos.. \index{Austin B.}Austin B.
\section{}is a real life spam filter. It would picture/geo tag / date bogus ads,  bad service (traffic, bars, restaurants, trains, cabs, newspapers).. \index{Dave T.}Dave T.
\section{}is a social parking exchange.  Get credit by giving up a spot on a high-value street.  Use credit 2 find the spots you want.. \index{Mark R.}Mark R.
\section{}is all about dogs! Dog-friendly parks and public spots,  check-in-based heatmaps for dog runs,  meet-up scheduling for doggie playdates.. \index{Carla E.}Carla E.
\section{}\index{crime!nearby}is like a CarFax for every street address: history of sale prices,  property values,  crimes,  building permits,  and sex offenders.. \index{Michael S.}Michael S.
\section{}is my personal concierge: it knows exactly what i like and can recommend an activity uniquely catered to me for any given day/time. \index{Zain Y.}Zain Y.
\section{}is smarter than google maps when it comes to best cab route in traffic.. \index{Randy L.}Randy L.
\section{}Keeps a Calendar of upcoming Events all over nyc,  It would be nice if it only showed event based on my interests. \index{Paige P.}Paige P.
\section{}keeps track of brokers and RE firms that falsely list 'no-fee' apartments on Craigslist and penalize them on CL for lying.. \index{Charles L.}Charles L.
\section{}Keeps track of how much I'm eating daily and reminds me of my daily calories intake goals. \index{Lissette R.}Lissette R.
\section{}learns my travel patterns around the city,  compares that to aggregate behavior,  \& suggests ways for me to change to save time + avoid crowds. \index{John G.}John G.
\section{}\index{Metrocard!fare evasion}\index{bus!riding without Metrocard}let me go inside the subways and buses without using my metrocard. \index{Nabil M.}Nabil M.
\section{}let's me announce when I need a babysitter to all my friends' babysitters and they can bid or respond to my announcement/s.. \index{dari y.}dari y.
\section{}let's me send information about streets that need repairs (potholes,  etc.). \index{Jake D.}Jake D.
\section{}Let's me use my smartphone as a  (and maybe MetroNorth?) - and let's it be refilled either automatically.. \index{U.N. O.}U.N. O.
\section{}Let's you 'hail' a cab,  and - if you want 'tweets' your location/destination for those nearby,  who might want to share the ride. \index{U.N. O.}U.N. O.
\section{}lets me browse geotagged historical photos,  audio and other media from the NYPL,  in the place I'm at.. \index{Anthony T.}Anthony T.
\section{}lets me check OUT of places,  not just check in.. \index{Kendall B.}Kendall B.
\section{}lets me conveniently and securely vote in elections,  referendums or opinion polls without paper ballots,  waiting in line or attending a meet. \index{elliot k.}elliot k.
\section{}lets me customize my taxi ride. When the ride starts I swipe my ccard,  and then shows info applicable to me,  including auto-mute : ). \index{Luis M.}Luis M.
\section{}lets me find a list of nearby,  certified babysitters and request them on the fly.. \index{Ahuman P.}Ahuman P.
\section{}lets me find people who want to go on a walk in the evening. \index{Simeon L.}Simeon L.
\section{}lets me know if an individual or business has recieved a payment from a political campaign in NYC.. \index{Charles L.}Charles L.
\section{}lets me know in realtime staten island ferry arrivals,  departures,  delays \& cancellations \& also weekend and holiday schedules.. \index{Candace K.}Candace K.
\section{}lets me know what retailers,  salons,  grocery stores and other services are open late.. \index{Victoria G.}Victoria G.
\section{}lets me make a geolocated 311 request from my phone,  with menu icons for the most common requests (pothole,  noise,  etc). \index{Justin L.}Justin L.
\section{}lets me post when I'm sick,  where \& what I ate recently.  This could help prevent food born illness,  flu outbreaks,  or worse.. \index{Dave T.}Dave T.
\section{}lets me put a geolocation bookmark in cool places in the city to check out later. Don't always have time to write it down then forget.. \index{Dave T.}Dave T.
\section{}lets me read and search every municipal labor contract.. \index{Ahuman P.}Ahuman P.
\section{}lets me record bike trip times,  jogging times,  and build routes for other bikers/joggers. Then everyone can compare / race for best times.. \index{Dave T.}Dave T.
\section{}lets me see retaurant health inspection reports right on my smartphone while I'm on the move!. \index{Stephen C.}Stephen C.
\section{}Lets me take a photo of a broken sidewalk,  a pothole,  or similar problem,  geo-tag it,  and submit it for repair.. \index{Gerald Philip M.}Gerald Philip M.
\section{}lets NYers look up how to properly dispose of any given item (throw out,  recycle,  compost,  donate,  etc) and identify where and when to do so. \index{Amy B.}Amy B.
\section{}\index{apps!referenced!Gowalla} \index{apps!referenced!Foursquare} lets people build and share their own siteseeing itinerary (foursquare/gowalla enabled),  and people can vote on which itineraries are best. \index{Luis M.}Luis M.
\section{}\index{bus!earn bus miles}lets people earn frequent bus miles,  and reward them with rebates or free bus passes. Promotes more use of public transportation.. \index{Luis M.}Luis M.
\section{}lets people earn frequent taxi miles,  and reward them with rebates or free taxi rides. You earn miles after you swipe your card in the cab. \index{Luis M.}Luis M.
\section{}lets people know the history and future projects related to the area in the city where they are standing or driving by.. \index{Lesley V.}Lesley V.
\section{}lets people post/view info to anything in the city,  a restaurant would have virtual notes by customers,  bus stop - service info,  etc.. \index{Lance N.}Lance N.
\section{}lets people share compelling photo opportunities (unique sightings,  monuments,  stills,  realtime events) based on location and time. \index{Jason J.}Jason J.
\section{}Lets people submit and vote on photos taken of NYC landmarks and events.. Its like voting for the best new postcard. \index{Luis M.}Luis M.
\section{}lets people wish they could check-in to a business or venue that is not there yet.. Lets us track business need in an area/community.. \index{Luis M.}Luis M.
\section{}lets tourists know when and where celebrities will be such as,  book signings and so forth.. \index{Millicent M.}Millicent M.
\section{}lets us crowdsource photographs,  tags,  and rate performance of NYC civil servants,  cops,  etc.. \index{Anthony T.}Anthony T.
\section{}lets us vote on the quality and condition of streets in NYC and based on the votes of users and residents,  speed up the repairs as needed.. \index{Kiran G.}Kiran G.
\section{}lets you 'like' or rate any street or block in the 5 boroughs. You could review their quality,  cleanliness,  safety,  noise,  etc.. \index{Carlos J.  G.}Carlos J.  G.
\section{}lets you know about live pick up sport games happening in your area.. \index{Ben S.}Ben S.
\section{}lets you put in cross streets and spits out local restaurants with rating by all the major food raters:  ZAGAT,  Chow Hound,  etc.. \index{Franco C.}Franco C.
\section{}lets you put in cross streets and spits out parking garages/lots  along with rates and availability. \index{Franco C.}Franco C.
\section{}Links language partners (students of different languages with native speakers). \index{Alexander P.}Alexander P.
\section{}Lists all elected officials and their role based on my current location. And,  the ability to email their office directly from the app.   Thi. \index{Daniel N.}Daniel N.
\section{}lists all free events and places in all boroughs. \index{Deborah R.}Deborah R.
\section{}lists all local brunches with unlimited mimosas \& bloody marys. \index{Kelly D.}Kelly D.
\section{}lists all New York City hotels that have had bed bugs and other infestations in the past six months.. \index{Rachel S.}Rachel S.
\section{}lists all restaurants' dining deals (i.e. 2-for-1,  free drink w/ meal,  etc.) for the day.. \index{Garrett Z.}Garrett Z.
\section{}lists all the FREE nights/dates at museums/galleries in the City w/ locations,  hrs,  travel suggestions,  maps \& user reviews. \index{Amanda A.}Amanda A.
\section{}lists all the street fairs and road closures for each particular day.. \index{Graham B.}Graham B.
\section{}lists apartments (or rooms in apts.) for short-term rental or swaps,  and also includes a bidding mechanism. \index{Jason G.}Jason G.
\section{}lists available apartments,  rental or sales prices and contact info,  and also lists going rental and sales costs for similar aparmtents.. \index{Deborah R.}Deborah R.
\section{}\index{GPS!fitness places}lists details about fitness facilities,  rec centers,  parks,  and provides directions based on GPS location.. \index{Deborah R.}Deborah R.
\section{}lists local laws and regulations we should know. (Regarding taxis going to Brooklyn,  smoking in parks,  riding a bike out of the bike lane.). \index{Edwin A.}Edwin A.
\section{}lists near by dog parks based on latitude/longitude. \index{Sze C.}Sze C.
\section{}lists nearby ATM machines based on their transaction fee. \index{Tom O.}Tom O.
\section{}lists times for garbage pickup near me. \index{Sze C.}Sze C.
\section{}\index{civic engagement!livestream from the steps of City Hall} livestreams whatever's happening on the steps of City Hall (see \& listen to demonstrations,  rallies). \index{Dawn M.}Dawn M.
\section{}locates all medical services in an area,  emergency or not,  (ie pharmacy,  ER,  doctor office) and lists their hours. \index{Paul G.}Paul G.
\section{}looks up NYC history using photos,  wikipedia,  gps,  and street names.. \index{Randy L.}Randy L.
\section{}makes all dog owners curb their dogs and pick their feces. It's disgusting to see and step on doggy poop by the sidewalk... \index{Carlos J.  G.}Carlos J.  G.
\section{}\index{superhero powers!obliterate cars with obnoxious alarms}makes it easy to inform the powers that be of cars with obnoxious alarms that blare incessantly. Or simply obliterates them at a touch.. \index{Louis R.}Louis R.
\section{}makes sense of NYC schools for parents -- locations,  when to apply,  report cards,  class size,  waiting lists and specialized curriculums.. \index{Will T.}Will T.
\section{}Makes suggestions for weekend activities,  deals,  shows,  etc based on the weather forecast and time of year. \index{Luis M.}Luis M.
\section{}Manages and customized visitors journey into the city, from getting discount,  to finding other visitors to enjoy their stay with. \index{Nickelson A.}Nickelson A.
\section{}maps ALL the service opportunities on www.nyc.gov/service. \index{Christina  V.}Christina  V.
\section{}maps alternate side parking days,  times and locations in real-time.. \index{Aric B.}Aric B.
\section{}maps available parking spots near me in real-time.. \index{Aric B.}Aric B.
\section{}maps city parks,  showing age range of equipment,  construction updates,  hours of operation and allows parents to rate parks. \index{Deirdre B.}Deirdre B.
\section{}\index{crime!map of every reported incident}maps every reported crime,  in the past and in real-time,  on the web and mobile.. \index{Michael S.}Michael S.
\section{}maps locations but is super specific i.e. if you hit the railroad tracks,  you've gone too far.. \index{Christina  V.}Christina  V.
\section{}maps out \& describes all the fun and interesting locations in movies,  shows,  books,  and historical events within the 5 boroughs. \index{Trev E.}Trev E.
\section{}maps out and lists all the cooling centers. \index{Sze C.}Sze C.
\section{}maps out the dryest path that I can take from point A to point B during a rainstorm.. \index{Gene L.}Gene L.
\section{}maps out the highest concentrations of speeding SUV drivers in each NYC borough. \index{Sze C.}Sze C.
\section{}maps traffic in real-time.. \index{Aric B.}Aric B.
\section{}maps user uploaded photos of bike lane infringements.. \index{Chris S.}Chris S.
\section{}\index{foodtrucks!ice cream} maps where food and ice cream trucks are throughout the city.. \index{Christina  V.}Christina  V.
\section{}navigates me indoor through exhibitions,  shopping malls,  museums,  train stations,  airport gates,  .... \index{Lars Gerd P.}Lars Gerd P.
\section{}\index{GPS!as a tour guide}navigates tourists through the city while giving them facts and history on each of the sites.  A GPS-enabled NYC tour guide.. \index{Matthew D.}Matthew D.
\section{}not only requests a taxi to go to your location but also lets you bid for taxis in areas where demand exceeds supply.. \index{New Y.}New Y.
\section{}notifies cab drivers that there services are needed and also gives an estimate of the price by calculating the route. \index{Darrian G.}Darrian G.
\section{}notifies me when people around my area need some help,  they can rise a red flag using same app n i can rise a white flag 2 tell dem am comin. \index{Mahesh S.}Mahesh S.
\section{}notifies me where there are places to donate clothes and household goods. \index{Emily M.}Emily M.
\section{}notifies people about their selective stores special sells on items and allows them to reserve them with a downpayment online .. \index{Darrian G.}Darrian G.
\section{}notifies people on job openings/ opportunities based on their profession and qualifications.. \index{Darrian G.}Darrian G.
\section{}NYC renters can anonymously share their address,  monthly rent,  and lease date. It will help future renters know the appropriate rental rates. \index{Michael M.}Michael M.
\section{}offers and looks for vacancy such as apartment for rent,  like a SNS. The provider get a reward when someone contracted apartment for rent.. \index{Hitoshi K.}Hitoshi K.
\section{}Organizes/announces public lectures and educational/ training events. \index{Alexander P.}Alexander P.
\section{}Pairs college students looking for jobs with businesses looking for employes. \index{Alexander P.}Alexander P.
\section{}Pairs local residents with other local residents for daily tasks like dog walking,  watering plants,  handy-man tasks. \index{Alexander P.}Alexander P.
\section{}pairs the parents of area students who need help with qualified tutors (college students,  etc).. \index{Norm R.}Norm R.
\section{}passively takes noise samples during the day,  combines low decibel readings from disparate phones to auto-file noise 'notices'.. \index{Justin H.}Justin H.
\section{}\index{realtime!traffic} pin points your location and shows real time traffic within a 5 mile radius.  (free iphone app) Avoid using 1010 wins. \index{Leo M.}Leo M.
\section{}\index{GPS!locations of products within big box stores}pinpoints a specific location of a product in a big box retailer based on GPS and inventory lists.  Gives you the aisle and guides you.. \index{Anthony O.}Anthony O.
\section{}\index{plan!trips to Westchester} \index{Westchester}plans trips between NYC and Westchester and NYC and New Jersey.. \index{Josie P.}Josie P.
\section{}Precisely calculates how much a cab ride will cost given the rate of speed and time. The cabulator.. \index{Will L.}Will L.
\section{}Prevents testing and driving. \index{Alexander P.}Alexander P.
\section{}\index{authoritarian streak!promote commuting groundrules}promotes more friendly/efficient commuting by groundrules (i.e. don't shove/block ppl exiting trains) w/incentives for imprvment/efficiency. \index{Christopher B.}Christopher B.
\section{}promotes only those businesses that actively pledge and demonstrate service to the NYC community and environment.. \index{Jay M.}Jay M.
\section{}provides a comprehensive and interactive calendar detailing items including city holidays,  major events,  and important deadlines.. \index{Scott K.}Scott K.
\section{}provides a geo-located,  real-time list of all free activities and giveaways (e.g.,  free concerts,  free food samples). \index{Jason G.}Jason G.
\section{}\index{bus!API}provides a open API to all MTA transit information,  schedules,  delays,  current location of trains and buses  information. \index{Kyri S.}Kyri S.
\section{}provides City route mapping with options to choose:  most direct,  least expensive,  public vs. private transportation,  fastest route based on. \index{Franco C.}Franco C.
\section{}provides easy access to all the great resources that are on NYC311 online.. \index{Evan T.}Evan T.
\section{}\index{medical!hospitals}provides information on public hospitals and their services. \index{Yauhen K.}Yauhen K.
\section{}provides list of tennis,  basketball,  football courts for reserving time slots and checking availability.. \index{Songul A.}Songul A.
\section{}provides ratings from the better business bureau for all NYC businesses,  not just restaurants. \index{Jason G.}Jason G.
\section{}\index{realtime!traffic}provides real time traffic delays with road work schedules. \index{Franco C.}Franco C.
\section{}provides translation services in popular languages so that tourist/immigrants can better use public services (e.g.,  transportation). \index{Jason G.}Jason G.
\section{}provides up to date bike routes throughout the city.  Bike maps are unwieldy when on a bike and typically out of date within a month.. \index{Amanda C.}Amanda C.
\section{}provides up-to-date data on the city's tax revenues,  projected expenditures,  and actual expenditures. \index{Dan K.}Dan K.
\section{}push notifications for amber alerts/criminal leads depending on location.. \index{Vicki T.}Vicki T.
\section{}puts Places w/ Faces in TimeEra of Users' choosing: e.g. 1960s Andy Warhol Union Square or 1950s Charlie Parker Tompkins Square Park,  etc.. \index{David K.}David K.
\section{}puts the info about when the next train will come on my phone -- so I know before going down into the station. \index{alisa b.}alisa b.
\section{}ranks playgrounds by the number of tickets and other police activity - cross reference by playground type (water,  etc) and location. \index{Rob F.}Rob F.
\section{}rates cab drivers.  I should be able to take a picture of their cab/id and rate them. Then search and contact cabs i like. \index{Paul V.}Paul V.
\section{}Rates NYC waiters of restaurants based in they kidness and professionalism.. \index{Valentina C.}Valentina C.
\section{}reads exact gps location \& lists the next two trains/buses that're departing within a five block radius with clickable simple map options.. \index{Daniel S.}Daniel S.
\section{}real time information on what streets have been closed for police action or construction(including traffic levels at any given intersection). \index{Walter C.}Walter C.
\section{}\index{camera!overlay historic images on current view}recognizes what the camera is seeing,  and then shows historic images of those streets and buildings throughout the decades.. \index{Deborah R.}Deborah R.
\section{}recommends things to do as a public service. 1) Optimizes city revenue. 2) Deliberately sends patrons to attractions that aren't solvent.. \index{Justin H.}Justin H.
\section{}recommends what clothes to wear and what accessories to bring according to weather conditions and temperature.. \index{James F.}James F.
\section{}\index{authoritarian streak!track hotel users by bluetooth}records bluetooth signatures of all phones in or entering hotels. Might discourage the trade because they'd be visible by frequency perday. \index{Justin H.}Justin H.
\section{}\index{taxis!fare calculator} \index{avoid!taxi ripoffs} records how much my cab fare was and how much it should've been (on average). By self policing we might avoid taxis ripping us off.. \index{Dave T.}Dave T.
\section{}reminds me daily to bring my umbrella or sunglasses depending on precipitation \% and UV ray statistics.. \index{Sarah T.}Sarah T.
\section{}replaces all my discount cards. The user scans some vouchers and after a certain amount of vouchers scanned,  the user gets a discount.. \index{Martin M.}Martin M.
\section{}\index{taxis!request pickup}requests a taxi come to my location now or at a specified time and I can offer an additional reward/tip if I'm really desperate or in a rush. \index{Patrick H.}Patrick H.
\section{}\index{shopping!show tickets}reserves broad way show/concert tickets for users who don't have to sit in front of a computer in order to get tickets.. \index{Vicki T.}Vicki T.
\section{}\index{construction info}reveals data about public construction projects containing the purpose,  start date,  end date,  violations,  department responsible,  etc.. \index{John D.}John D.
\section{}\index{shopping!Craigslist scanner}Scans craigslist for Neighborhood relevant listings. \index{Alexander P.}Alexander P.
\section{}\index{hookups!people from same country}search people come from same country. \index{Uenishi M.}Uenishi M.
\section{}\index{shopping!sales near me}searches for sales and coupons for stores near my location.. \index{Rachel S.}Rachel S.
\section{}Sells electronic's like a ebay for people in ny and in your area. You list what you demand or post what you want to sell.. \index{Alex M.}Alex M.
\section{}sends me an email message when one of my favorite movies hits the theaters and then is released on dvd. \index{andreas t.}andreas t.
\section{}sends out snow ban and alt. street parking alerts based on a location that you can set using GPS while in your car.. \index{Steven H.}Steven H.
\section{}Sends the subway service changes to my phone each morning.. \index{Kris M.}Kris M.
\section{}\index{hookups!shakes around single firls}shakes whenever there is a single girl in the bar. \index{Aalap S.}Aalap S.
\section{}show me people around me and launch a question about that place and receive answers in real time.. \index{Josue G.}Josue G.
\section{}\index{restrooms!show and rate}shows / rates nearby restrooms.. \index{R B.}R B.
\section{}\index{kids!things to do with}shows / rates things to do with kids that day in NYC.. \index{R B.}R B.
\section{}\index{useful info!government contacts}shows a dashboard of all NYC government contacts (phone,  email,  twitter). \index{\index{Saul S.}}\index{Saul S.}
\section{}shows a list of lunch specials within 5 blocks of where I work. \index{Laura B.}Laura B.
\section{}\index{safety!at different times of day}shows a NY map (showing districts: like SoHo) that rates the safety of neighborhoods at diff times of day. Can be rated by gov and/or public. \index{Niko D.}Niko D.
\section{}shows accessiblity information (e.g. ramps/elevators) for public transportation on a map based on location. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}\index{Donkey Kong reference} \index{food cart finder} shows all nearby food carts hours and location. The app could be called Food Kart Madness (think DK Country 2). Also,  a Surpise me feature. \index{Ethan P.}Ethan P.
\section{}shows all of NYC's workspaces and incubators.. \index{Alex H.}Alex H.
\section{}Shows all unbiased real estate listings,  including square footage,  clean un-stretched photos,  previous tenant reviews,  bldg code violations. \index{John M.}John M.
\section{}\index{augmented reality!skyline}shows an augmented reality view of the skyline as it would appear if all known construction were complete. \index{Sarah H.}Sarah H.
\section{}\index{restrooms!find clean} shows clean public restrooms. \index{Lorissa S.}Lorissa S.
\section{}\index{crime!NYPD stats}Shows daily (or monthly) \index{agency!NYPD} NYPD crime stats by borough and citywide for the past 20 years using a heatmap or graph.\index{Gary R.} Gary R.
\section{}\index{by cuisine!pizza}shows how nearby pizza places are,  with price ,  comments and quality ranking.. \index{Hugo C.}Hugo C.
\section{}\index{camera!hidden}shows in real-time hidden cameras of different sights in NYC. \index{Valentina C.}Valentina C.
\section{}\index{shopping!music instruments}shows me all music instrument stores in NYC. \index{Heidi F.}Heidi F.
\section{}\index{shopping!sample sales}shows me all sample sales that are going on.. \index{Vicki T.}Vicki T.
\section{}shows me all the available datasets published by the City and allow me to mash it up myself. \index{J N.}J N.
\section{}shows me alternate parking rules of any given street. I can enter an address of look up on a map.. \index{Ana M.}Ana M.
\section{}shows me an overview of the best upcoming events near my location. Comedy sows,  live music,  movies,  parades...all that makes the day special. \index{David U.}David U.
\section{}shows me available taxis near me. \index{Noah D.}Noah D.
\section{}shows me daily deals in NYC - based on my area(s) of interest.. \index{R B.}R B.
\section{}\index{bus!status of}shows me detailed transit status and schedules for busses and subways. \index{Jake D.}Jake D.
\section{}\index{bus!location of}shows me exactly where the buses and subways are,  not when they are scheduled. riders can checkin to help determine where the bus/train is.. \index{rich r.}rich r.
\section{}\index{sports!free courts} shows me if there are any free basketball,  tennis,  handball,  etc courts. \index{Eric C.}Eric C.
\section{}shows me list of apartments I can crash into for a day (maybe night as well) (while the owner is out for work,  travel etc).. \index{Tinku K.}Tinku K.
\section{}\index{bus!location of}Shows me on Google Maps exactly ~where~ my bus is via GPS.. \index{Dave M.}Dave M.
\section{}shows me places that are marked by GPS that are still open when on a night out. \index{Sandeep G.}Sandeep G.
\section{}\index{transit!real time info}shows me real time information on public transits. \index{Josiah L.}Josiah L.
\section{}\index{noise!in restaurants}shows me restaurants by noise levels (this is a big deal for my aging parents!) and other ratings. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}shows me restaurants with vegetarian options. \index{Matt S.}Matt S.
\section{}\index{shopping!best flower shops} \index{best!flower shops}shows me the best flower shops for delivery of floral arrangements,  by neighborhood,  with customer feedback. \index{chris n.}chris n.
\section{}\index{by cuisine!pizza}\index{best!pizza}shows me the best pizza around me with reviews and pictures. \index{Harry L.}Harry L.
\section{}shows me the current deals that are offered in restaurants,  stores(15\% off),  bars(happy hours) etc based on my current time and geo-location. \index{Aanchal J.}Aanchal J.
\section{}shows me the location of famous films sets. \index{Robert L.}Robert L.
\section{}\index{find the closest!public drinking fountain}shows me the locations of all public drinking fountains.. \index{Joel K.}Joel K.
\section{}shows me the nearest apartments for rent by my GPS location and other apartment rental preferences. \index{Andrew C.}Andrew C.
\section{}shows me the nearest fashion retail stores that on sale to make shopping in NYC much more fun.. \index{Nisa G.}Nisa G.
\section{}shows me the places. \index{daniely v.}daniely v.
\section{}\index{hookups!realtime bar demographics} shows me the real-time demographics of bars \& clubs (how crowded,  number of males/females,  their ages and zip codes). \index{Ben  S.}Ben  S.
\section{}shows me what different locksmiths will charge me for their services.. \index{Victoria G.}Victoria G.
\section{}\index{augmented reality!what am I seeing out of the window} shows me what I can see out from any window in Manhattan. \index{Robert L.}Robert L.
\section{}\index{food trucks!geolocator}Shows me where all of the great food trucks are parked at that time,  based on geolocation.. \index{Dylan H.}Dylan H.
\section{}\index{plan a walking route under scaffolding}shows me where all the city's scaffolding is,  so I can plan a walking route without needing an umbrella.. \index{Ben T.}Ben T.
\section{}shows me where all the photography / art exhibits are going on.. \index{Ricky C.}Ricky C.
\section{}shows me where and for how much money I can get regular menu dish to be sated which is close to me. \index{ilia d.}ilia d.
\section{}shows me where community gardens and urban farms are,  and offers horticultural tips,  tutorials and social opportunities once i get there. \index{Anthony T.}Anthony T.
\section{}shows me where famous people are. \index{Judy H.}Judy H.
\section{}Shows me where the cable guy currently is and predicts what time he'll arrive.. \index{Doug P.}Doug P.
\section{}\index{restrooms!ratings of}shows me where the closet public toilet is,  and lets users tag and rate it on various characteristics.. \index{Anthony T.}Anthony T.
\section{}\index{taxi!locate nearest} shows me where the nearest available taxi is.. \index{Nikki S.}Nikki S.
\section{}Shows monthly or daily FDNY response times by borough and by city for the past 20 years.\index{Gary R.} Gary R.
\section{}\index{GPS!real estate for sale} shows near by Real Estate for sale or rent based on my GPS location or by typing in an address.. \index{Steven H.}Steven H.
\section{}shows nearby green markets (includes information on how to sell at a green market). \index{Sze C.}Sze C.
\section{}shows nearby public (or semi-public) restroom/toilet. \index{Boy A.}Boy A.
\section{}shows nearby recycling bins for bottles,  cans,  and/or paper products. \index{Sze C.}Sze C.
\section{}\index{GPS!find emergency rooms} \index{medical!hospitals} shows nearest walk in clinic or emergency room to my location via gps.. \index{Rhonda D.}Rhonda D.
\section{}shows neighborhood amenities and ratings by people who live in the neighborhood for apartment hunters.. \index{Rhonda D.}Rhonda D.
\section{}\index{realtime!queues at tourist attractions} shows queueing times in realtime for various tourist attractions,  events or restaurants by registering how many are in the queue. \index{Andreas G.}Andreas G.
\section{}\index{bus!arrival countdown}shows real-time passenger information (RTPI) such as estimated arrival time for buses at bus stops.  Hate waiting for the bus.. \index{Ronan H.}Ronan H.
\section{}shows realtime (actual \& estim.) population density so I can go places at the optimal times... like Google traffic but for human bodies.. \index{Chris S.}Chris S.
\section{}\index{crime!pertient info on perps}shows recent crimes in your current location along with pertinent info on the perps.  Thanks.. \index{Richard V.}Richard V.
\section{}\index{subway!location of}shows subway train locations (displays like the one being piloted on the Canarsie Line) and time to the next train.. \index{celentha f.}celentha f.
\section{}\index{best!place to grab a cab} \index{taxis!finder} shows the best place to try and grab a cab from where I'm located.. \index{R B.}R B.
\section{}shows the daily/hourly sea levels surrounding Manhattan with snapshot of current weather data.\index{Gary R.} Gary R.
\section{}\index{hookups!exclusive date spots} shows the exclusive,  cheap or not,  date spot to impress people through scenary. \index{ray m.}ray m.
\section{}shows the nearest Hertz connect and/or Zipcar locations with available vehicles within a short walking distance. \index{\index{Sheryl C.} Sheryl C.}\index{Sheryl C.} Sheryl C.
\section{}\index{bus!location of}\index{subway!location of}shows us the live location of subways and buses on all lines.. \index{Deborah R.}Deborah R.
\section{}shows water use by building,  cuz quick drop in the winter probably means the boiler went out= I don't want to live there.. \index{Justin H.}Justin H.
\section{}shows what NYC looked like in 1940.  It would be powered by the 1939-41 Tax Photographs taken of all five boroughs... \index{Will T.}Will T.
\section{}shows what streets are closed and why.. \index{Edwin A.}Edwin A.
\section{}shows where and when I can see firworks throughout the year in NYC.. \index{Chris S.}Chris S.
\section{}shows where deli-ban is. \index{Kosuke N.}Kosuke N.
\section{}\index{bus!location of}shows where MTA bus is running at in MAP. \index{Kosuke N.}Kosuke N.
\section{}shows which show is being filmed on my street.. \index{Cemre G.}Cemre G.
\section{}\index{sports!all events happening right now} shows you all the sporting events happening in the city at that moment.  High school,  college,  profesional. So hard to find this info now.. \index{john h.}john h.
\section{}\index{medical!track my insurance info} stores my basic health \& insurance info that I could bring to any Dr/Pharmacy/Hospital in the city so no forms.. \index{Paul G.}Paul G.
\section{}Streams live local events (video and/or audio) to my devise ahead of me arriving at the event. \index{Robert L.}Robert L.
\section{}suggests activities of interest around the city based on a person's facebook profile.. \index{Rachel S.}Rachel S.
\section{}suggests similar restaurants nearby when the place I go to is full.. \index{Randy L.}Randy L.
\section{}syncs with the MTA's real-time train information so I know when my train will arrive and if there are delays.. \index{New Y.}New Y.
\section{}tags commercial establishments by languages spoken to improve foreign tourist experience and foster stronger ethnic neighborhood identity. \index{Eduardo M.}Eduardo M.
\section{}\index{crime!submit evidence}takes the see something say something mobile. Post pics/vids to the web,  allos users to vote on issues,  \& sends crime evidence to the \index{agency!NYPD}NYPD. \index{Amit P.}Amit P.
\section{}\index{best!standing location for subway exit} tell you where to stand on commuter rail (e.g.,  Metro North,  LIRR,  PATH,  etc.) to get to the best exit at your stop. \index{Richard L.}Richard L.
\section{}telll me peoples names,  since  it is so crowded and you meet new people everyday. It should work like \index{apps!referenced!Shazam} shazam,  but recognizing faces.. \index{Alfonso B.}Alfonso B.
\section{}Tells a story based on GPS. 8+ million New Yorkers can tell their story \& visitors can listen in on what happened there,  vote,  share,  etc.. \index{Todd B.}Todd B.
\section{}tells devs what APIs and data are available to utilize so we can build some of these great ideas!. \index{Christopher B.}Christopher B.
\section{}\index{bus!arrival countdown}Tells how far away the next city bus is from the stop I'm standing at. \index{Kyri S.}Kyri S.
\section{}\index{train!location of}Tells me (in real time) when a train will arrive and exactly where it is when I check.. \index{Jason W.}Jason W.
\section{}\index{shopping!sale finder}tells me about sales in stores in my area. \index{Jessica K.}Jessica K.
\section{}\index{restrooms!find clean}tells me clean public toilet around me. \index{Kosuke N.}Kosuke N.
\section{}\index{tour guide}tells me cool facts about NYC as I explore. Like having my own personal tour guide.. \index{Tedde T.}Tedde T.
\section{}tells me current waiting times for the most popular long-wait places in NYC: Shake Shack,  TKTS,  Magnolia,   Emp St Bldg,  Top of the Rock etc. \index{Jeff S.}Jeff S.
\section{}\index{medical!nearest doctor with my insurance}tells me doctor/clinic covered by my insurance around me. \index{Kosuke N.}Kosuke N.
\section{}\index{apps!referenced!Foursquare} tells me historic facts/pop culture about my location when I check into foursquare. \index{amanda f.}amanda f.
\section{}Tells me how many dogs are in the dog run at any given time. \index{Shawn V.}Shawn V.
\section{}\index{value of public works} tells me how public services / goods were funded and at what cost. Then lets me vote afterwards on whether it was worth it.. \index{Dave T.}Dave T.
\section{}\index{Greenmarkets} tells me hrs/location/products/farmers available at all Greenmarkets \& gives me travel suggestions w/ google maps so I can get there quickly. \index{Amanda A.}Amanda A.
\section{}\index{parking!safe duration} tells me if,  and how long,  it is safe to park at any given point at any given time. Down with unfair parking tickets!. \index{Jennifer S.}Jennifer S.
\section{}\index{kids!friendly restaurant}tells me kids-friendly restaurant. \index{Kosuke N.}Kosuke N.
\section{}\index{food!restaurant inspections} \index{GPS!details of restaurant letter grades} Tells me the Letter Grade and Date of Last Inspection for any restaurant based on my GPS location + search.. \index{Randy L.}Randy L.
\section{}\index{realtime!energy consumption}tells me the real-time energy consumption of anything i point my phone at - me,  a vehicle,  a building,  etc. \index{Anthony T.}Anthony T.
\section{}\index{realtime!arrivals} Tells me the trains (and busses) are scheduled to arrive at a selected stop/station during the next 1/2 hr or so.. \index{U.N. O.}U.N. O.
\section{}\index{bus!local services}tells me what buses stop nearby and when the next one should arrive.. \index{Steve K.}Steve K.
\section{}\index{civic engagement!local districts}tells me what council district,  community board,  police precinct,  etc that I'm in \& provides relevant \& timely information about each. \index{Philip A.}Philip A.
\section{}tells me what event is going on near me at any given time. Is that music I hear? What is that? A concert? Wish I had some info!. \index{Zoli H.}Zoli H.
\section{}\index{music!radio playlists} tells me what radio stations are playing what songs at that moment. \index{peter w.}peter w.
\section{}tells me what street fairs/events are going on in the five boroughs that day.. \index{Jennifer F.}Jennifer F.
\section{}\index{what time is!rush hour at a particular station}tells me what time is rush hour at a particular station and on a particular line (subways and buses). \index{Nabil M.}Nabil M.
\section{}\index{avoiding!protests} tells me when protests / demonstrations are scheduled so I can avoid or take part. I Don't follow politics much so I never know these things. \index{Dave T.}Dave T.
\section{}\index{realtime!subway}tells me when the next subway car is to arrive at my station (before I go underground).. \index{stephen m.}stephen m.
\section{}\index{realtime!train}tells me when the next train is coming. \index{Steve B.}Steve B.
\section{}\index{realtime!subway}tells me when the subway will arrive at my station (particularly at night or on weekends). \index{Dave R.}Dave R.
\section{}\index{bathrooms!accessible}tells me where accessible bathrooms are around me,  how long the lines are,  and whether the staff glares at you if you don't buy something.. \index{John G.}John G.
\section{}\index{Greenmarkets}tells me where all the greenmarkets are,  no matter how small or large.. \index{Christina  V.}Christina  V.
\section{}Tells me where all the trains are so I know whether I'm better off walking 3 blocks to the F or 6 blocks to the R.. \index{Tim A.}Tim A.
\section{}\index{bus!location of}tells me where buses and trains are and when they'll be arriving at specific stops. \index{cooper f.}cooper f.
\section{}\index{parking!find free}tells me where free parking spaces are.. \index{bob b.}bob b.
\section{}tells me where I can \index{find!free restroom} \index{restrooms!free or not} find a bathroom (and if it's public or I have to purchase an item). \index{Hunter H.}Hunter H.
\section{}\index{sports!pickup games}tells me where I can go check out a neighborhood or pick-up soccer,  rugby,  lacrosse,  baseball game,  etc. \index{Celina D.}Celina D.
\section{}\index{shopping!sample sales}tells me where sample-sales is happening. \index{Kosuke N.}Kosuke N.
\section{}tells me where the water fountains are so I can easily refill my water bottle and cut down on bottled water!. \index{Bix A.}Bix A.
\section{}Tells me whether I have parked the legally mandated distance from a fire hydrant so that I don't receive a ticket based on an office's eyeba. \index{Jason G.}Jason G.
\section{}tells me which beaches are closed or have swimming advisories in the summer.. \index{Celina D.}Celina D.
\section{}tells me which subway car to ride so it takes me to the appropriate exit/subway transfer/handicap elevator at my final destination.. \index{Yumi K.}Yumi K.
\section{}tells us what's in the food served at schools and restaurants: Sugar,  Salt,  Yuk-Fat,  and Calories as well as Alllergens. \index{Laurent A.}Laurent A.
\section{}\index{realtime|escalators and elevators}tells where all escalator and elevator options are for subways AND which are NOT currently in service. It would need to update in real time.. \index{Rhonda D.}Rhonda D.
\section{}\index{food truck!lines at}tells where the food trucks are and how long the line is at each. \index{Richard L.}Richard L.
\section{}tells where the street fairs are and what events/food are available. \index{Richard L.}Richard L.
\section{}\index{calories burned per block walked}tells you exactly how many calories you burn per city block walked.. \index{Anna H.}Anna H.
\section{}\index{best!clubs,  lines at} tells you how long lines are to the best clubs/drink specials/cover/etc. PLEASE!. \index{Katie C.}Katie C.
\section{}\index{real estate!rent and availability}tells you the price rent and available real estate in any building based on my location. \index{Katy J.}Katy J.
\section{}\index{shopping!sample sales}Tells you were all the current retail sales are including sample sales. \index{Dana H.}Dana H.
\section{}\index{artistic value,  rank of}tells you what ranking you are in the country for thing.i.e... artistic value. \index{Kayla M.}Kayla M.
\section{}\index{map!subway in real time}tells you when the next train is coming before you are on the platforms,  especially Penn station 1, 2, 3, subway lines. \index{Susan S.}Susan S.
\section{}tells you where movies and TV shows are filming RIGHT NOW.. \index{Anna H.}Anna H.
\section{}Tells you who really owns that apartment,  and links you to prior complaints for that property.. \index{Charles L.}Charles L.
\section{}\index{job search}that aggregates job Searches using my specific preferences and would automatically send my resume and/or cover letter files to my picks.. \index{Sharto P.}Sharto P.
\section{}that connects small businesses in search for a small office space and allows them to combine their efforts and share 1 space.. \index{Anthony O.}Anthony O.
\section{}that contain a administrative portal dedicated to NYC which helps NYC people with information they want in critical position.. \index{srikanth k.}srikanth k.
\section{}\index{give me!biking directions}that gives directions for cyclists and shows all the bike paths in the city.. \index{David F.}David F.
\section{}that layers the voting record of city council members against donors who helped finance their election campaigns.. \index{paul m.}paul m.
\section{}\index{borrow or swap}that lets you borrow or swap things from people near you.. \index{Ben S.}Ben S.
\section{}\index{tell me!free cultural events}that tell me all the galleries openings and free cultural events. \index{Valentina C.}Valentina C.
\section{}\index{hookups!chat without revealing private information}that will allow me to chat with anyone in the same store,  bar or park real-time. without revealing private information.. \index{Diego M.}Diego M.
\section{}the tourists from around the world can easily pay there bills may be of hotel,  taxi and same kind of stuffs with the help of a NYC pay card. \index{Shivendra D.}Shivendra D.
\section{}to create virtual parades where busy people can join to support a cause.. \index{Valentina C.}Valentina C.
\section{}to find NYC gov sponsored events - concerts,  art installations,  street fairs. \index{Eric J.}Eric J.
\section{}Tracks real ratings of apartments... it can't be this hard to find an apartment in NYC. \index{Zachary B.}Zachary B.
\section{}\index{map!buses in real time}\index{bus!location of}tracks real-time locations of MTA buses on a zoomable map.. \index{Jennifer B.}Jennifer B.
\section{}\index{find my!stolen phone}tracks your phone or device if it is stolen. If near a wi-fi hot spot.. \index{Alex M.}Alex M.
\section{}Transfer of technologies compatibles with environment ESTs. \index{Jean-robert N.}Jean-robert N.
\section{}\index{voting!use of smart phones}transforms mobile smart phones and tablets‚ into secure,  authenticated location-based voting machines for a. \index{elliot k.}elliot k.
\section{}\index{subway!as snowboarding challenge} \index{sport!riding subway as}turns my subway commute into a snowboarding challenge where people are encouraged to stand while maintaining balance within the subway car.. \index{Gene L.}Gene L.
\section{}\index{sports!golf}turns our mobile devices into putters so that we can play a crazy 18-hole miniature golf game around the city. \index{Gene L.}Gene L.
\section{}\index{sports!on screen in back of cabs}turns the cab screen into a game center.. so I can challenge other cab riders in connect4,  tic-tac-toe,  checkers,  etc.. quick \& easy. \index{Luis M.}Luis M.
\section{}turns the city into a game and encourages people to discover new parts of the city. (kind of like Find the Future at NYPL). \index{Jonathan B.}Jonathan B.
\section{}\index{GPS!find a taxi with}\index{bus!location of}Use GPS locators to show real time location of city buses,  subway,  and cabs (if the cab co.s are willing) making it easier to get around.. \index{Steven H.}Steven H.
\section{}\index{phone!as Metrocard} \index{Metrocard!via phone}Use my phone as metro card. \index{Juanma O.}Juanma O.
\section{}users can freely share their new ideas and vote,  just like a BigAppsIdeas-all-the-time. \index{Xiaofei W.}Xiaofei W.
\section{}\index{augmented reality!people I meet and their political contributions}uses Augmented Reality and image (face/facade) recognition to show me the political contributions of people I meet and business I patronize. \index{Anthony T.}Anthony T.
\section{}\index{augmented reality!health inspections}uses augmented reality to overlay restaurants with their (not always posted) health inspection scores.. \index{Benjamin H.}Benjamin H.
\section{}\index{GPS!suggesting activities with}uses my foursquare history + gps + public event calendars to suggest nearby activities.. \index{Randy L.}Randy L.
\section{}\index{intuitive!pothole detection}uses my phone's accelerometer to detect potholes and automatically send the location to the DOT. \index{William K.}William K.
\section{}warns me when \index{ex-boyfriend warning}ex-boyfriends are in the vicinity.. \index{Dorothy J.}Dorothy J.
\section{}welcomes NYC visitors by linking most visited web sites...City Hotlines,  Parks,  Museums,  Theaters,  Parking,  Weather,  Zagat,  Biking etc.. \index{Robert G.}Robert G.
\section{}\index{911}when you call 911,  you are issued a reference number,  you enter the reference number in the app,  and track the responding vehicle and status. \index{Chad R.}Chad R.
\section{}which tells me the history of an artifact if i take a picture of it in any NY museum!!! cool!. \index{Mahesh S.}Mahesh S.
\section{}\index{shopping!nearby deals when driving}while travelling in your car,  your mobi prompts you the deals nearby 1km \& if you have item in your wish list , it also prompts nearby shop. \index{Prabhjit S.}Prabhjit S.
\section{}will allow a prospective renter to read any and all information about the building owner/manager,  tenants, and living conditions. \index{SHIRLEY F.}SHIRLEY F.
\section{}will help MTA do their job more efficiently and happily.. \index{Sze C.}Sze C.
\section{}will keep track of fun,  random activities on my bucket list that I can shake when I'm bored and go do!. \index{Sara D.}Sara D.
\section{}\index{bus!trip planning}will plot the fastest route from point A to B using MTA subways and buses,  using realtime bus and train positions and incl. transfer info. \index{Scott P.}Scott P.
\section{}Will provide refilling the metro card via a mobile device using you credit card. Thus,  long queues during peak hours can be avoided.. \index{\index{Sannidhi J.}Sannidhi J.}\index{Sannidhi J.}Sannidhi J.
\section{}Will scan the metrocard using any information available on it (barcodes or digits) \& display the avail balance,  thus avoiding long queues. \index{\index{Sannidhi J.}Sannidhi J.}\index{Sannidhi J.}Sannidhi J.
\section{}\index{best!dining options} will show best dinning and things to do when visiting places. \index{\index{cameron h.}cameron h.}\index{cameron h.}cameron h.
\section{}\index{best!Foursquare places} will show me the best places to visit through foursquare and gowalla. \index{\index{erin m.}erin m.}\index{erin m.}erin m.
\section{}will tell me all the specials offered in New York restaurants so i dont have to listen to them from the waiters.. \index{\index{Jose H.}Jose H.}\index{Jose H.}Jose H.
\section{}will tell me which deli's around NY offers what im looking for at anytime. This will help Deli businesses to promote themselves. \index{Jose H.}Jose H.
\section{}\index{map!of free wifi}with a map of free wifi based on my location. \index{\index{Ruthie V.}Ruthie V.}\index{Ruthie V.}Ruthie V.
\section{}with wifi access could integrate in real time all the cultural activities of the city,  through several tours by day and by night. \index{Jose c.}Jose c.
\section{}works just like SeeClickFix,  except that the city uses it as the official QOL reporting app.  Actually,  they should just use SeeClickFix.. \index{Maxwell P.}Maxwell P.
\section{}works like a RedMaps map. \index{Arthur R.}Arthur R.
\section{}works with ALL mobile operating systems,  like Symbian and WebOS,  as well as the dominant iPhone,  Android,  Blackberry,  and Windows 7. \index{Wendy S.}Wendy S.
\section{}Would let you find \index{discounts}discounts from mom \& pop stores,  and stores owned by our neighbors,  rather than out-of-town owned \& operated chains. \index{U.N. O.}U.N. O.
\section{}would provide 3 options of transportation, driving directions(for you or your cab), and ETA using real time traffic and public transportation.. \index{Abbe L.}Abbe L.